Learning growth mechanisms of tail realistic preferential attachment models from network degree distributions

### 2025-09-28 Files/paper.qmd
Fixing plots

textsize = 5
lwd = 1
ggplot() +
  geom_line(aes(x=x,y= y3), lwd=lwd) + 
  geom_segment(aes(x=k0, y=0.3,yend=eps + k0^a), lty=2, lwd=lwd)+
  geom_text(aes(x=k0, y=0, label='k[0]'), parse = TRUE, size=textsize)+
  geom_text(aes(x=6.3, y=4.3, label='beta'), parse=TRUE, size=textsize)+
  stat_brace(aes(x=c(0, 0), y=c(0, eps)), rotate=90, width=0.2)+
  geom_text(aes(x=0.3, y=eps/2, label='epsilon'), parse=TRUE, size=textsize)+
  theme_bw() + xlab('Degree')+ylab('Preference') + ylim(0,6)+
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(), legend.position='bottom')

>>>>

textsize = 5
lwd = 1
ggplot() +
  geom_line(aes(x=x,y= y3), lwd=lwd) + 
  geom_segment(aes(x=k0, y=0.3,yend=eps + k0^a), lty=2, lwd=lwd)+
  geom_text(aes(x=k0, y=0, label='k[0]'), parse = TRUE, size=textsize)+
  geom_text(aes(x=6.3, y=4.3, label='beta'), parse=TRUE, size=textsize)+
  stat_brace(aes(x=c(0, 0), y=c(0, eps)), rotate=90, width=0.2)+
  geom_text(aes(x=0.5, y=eps/2, label='epsilon'), parse=TRUE, size=textsize)+
  theme_bw() + xlab('Degree')+ylab('Preference') + ylim(0,6)+
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(), legend.position='bottom')
